---
title: "Creating graphs in R with `ggplot2`"
author: "Sarah McCutcheon"
date: "1/20/2022"
output: html_document
---

#Plots with ggplot2

We are going to make plot sin R and it's going to be amazing.

We use the following data from the Santa Barbara Coastal Term Ecological Research and National  Oceanic and Atmospheric Administration in our analyses

```{r echo=FALSE, message=FALSE}
#Attach packages
library(tidyverse)
library(readxl)
library(here)
```


```{r echo=FALSE, message=FALSE}
ca_np <- read_csv(here("data", "ca_np.csv"))

ci_np <- read_excel(here("data", "ci_np.xlsx"))

```

#Let's make graphs
```{r results='hide'}

ggplot(data = ci_np, aes(x = year, y = visitors)) +
  geom_line()

gg_base<- ggplot(data = ci_np, aes(x = year, y = visitors))

gg_base +
  geom_point()

gg_base +
  geom_col()

gg_base +  
  geom_area()

```

#Customize graphs

```{r}

gg_base +
  geom_line(
    color = "purple",
    linetype = "dashed"
  )

gg_base + 
  geom_point(color = "purple",
             pch = 17,
             size = 4,
             alpha = 0.5)

gg_base +
  geom_col(color = "purple4", fill = "mediumspringgreen")
```

#Mapping variables onto aesthetics

```{r}
gg_base + 
  geom_point(
    aes(size = visitors,
        color = visitors),
    alpha = 0.5
  )

gg_base + 
  geom_col(aes(fill = visitors))
```

#ggplot complete themes

```{r}
gg_base +
  geom_point(
    aes(size = visitors,
        color = visitors),
    alpha = 0.5
  ) +
  theme_minimal()
#labels
gg_base +
  geom_line(linetype = "dotted") +
  theme_bw() +
  labs(
    x = "Year",
    y = "Annual park visitors",
    title = "Channel Islands NP Visitation",
    subtitle = "(1963 - 2016)"
  )

#point and line graph

gg_base +
  geom_line(color = "purple") +
  geom_point(color = "orange",
             aes(size = year),
             alpha = 0.5)

#Multi-series

ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name)) +
  geom_line()

#Storing base code
gg_np <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name))
```

#Faceting ggplot graphs
```{r}
gg_np +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "year", y = "annual visitors") +
  facet_wrap(~ park_name)
```

#Saving/Exporting
```{r}
ggsave(here("figures", "np_graph.jpg"), dpi = 180, width = 8, height = 7)
```

